Multi-Resolution Spatio-Temporal Neural Field Estimation

### 2011-03-08 Multiresolution_framework/ltx/manuscript.tex
made some awesome changes that will blow your minds

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Multi-resolution \parham{spatio-temporal} Neural Field Estimation }

@@

The vectors of the kernel and the field scaling and wavelet functions, $\boldsymbol\lambda$ and $\boldsymbol\mu$, respectively, are defined by
\begin{align}
&\boldsymbol\lambda^\top(s)=[
	\begin{array}{ccccc}
		 \boldsymbol\phi_{j_0}^\top(s) & \boldsymbol\psi_{j_0}^\top(s) & \boldsymbol\psi_{j_0+1}^\top(s) & \cdots & \boldsymbol\psi_{j}^\top(s)
		\end{array}
		] \label{KernelBasisVector} \\
&\boldsymbol\mu^\top (r)= [
			\begin{array}{ccccc}
				\boldsymbol\phi_{j_0}^\top(r) & \boldsymbol\psi_{j_0}^\top(r) & \boldsymbol\psi_{j_0+1}^\top(r) & \cdots & \boldsymbol\psi_{j}^\top(r) 
			\end{array} 
				],
\label{FieldBasisVector}
\end{align}
where $s=r-r'$. The vectors in  (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in  (\ref{KernelWeights}) and (\ref{FieldWeights}).

@@

  \mike{The framework makes two key assumptions about the cortex: a linear activation function and stationary dynamics. Our main aim for this framework is to relax these assumptions using the multi-resolution decomposition. \dean{(our main aim wasn't really to relax the assumptions. if it was, we failed.)} While the decomposition itself holds, efficiently performing nonlinear smoothing in the much larger state space remains a challenge. Additional avenues for future work include extending the model to capture a second order synaptic response kernel, and time delays \parham{at lower spatial resolutions}.  The estimation techniques should also be extended to deal with spatial and temporal heterogeneity in the kernel. Finally, the majority of our current work involves applying this framework to collected data, primarily for the use of seizure detection and mitigation.}

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{Multi-Resolution Spatio-Temporal Neural Field Estimation }

@@

The vectors of the kernel and the field scaling and wavelet functions, $\boldsymbol\lambda$ and $\boldsymbol\mu$, respectively, are defined by
\begin{equation}
    \label{KernelBasisVector}
    \boldsymbol\lambda^\top(s)=[
    \boldsymbol\phi_{j_0}^\top(s) ~
    \boldsymbol\psi_{j_0}^\top(s) ~ 
    \boldsymbol\psi_{j_0+1}^\top(s) ~
    \cdots ~
    \boldsymbol\psi_{j}^\top(s)]
\end{equation} 
\begin{equation}
    \label{FieldBasisVector}
    \boldsymbol\mu^\top (r) = [
    \boldsymbol\phi_{j_0}^\top(r) ~ 
    \boldsymbol\psi_{j_0}^\top(r) ~ 
    \boldsymbol\psi_{j_0+1}^\top(r) ~ 
    \cdots ~ 
    \boldsymbol\psi_{j}^\top(r)
]   
\end{equation}

where $s=r-r'$. The vectors in  (\ref{KernelBasisVector}) and (\ref{FieldBasisVector}) are constructed in the same manner as the vectors in  (\ref{KernelWeights}) and (\ref{FieldWeights}).

@@

  \mike{The framework makes two key assumptions about the cortex: a linear activation function and stationary dynamics. Our main aim for this framework in the future is to relax these assumptions using the multi-resolution decomposition. While the decomposition itself holds, efficiently performing nonlinear smoothing in the much larger state space remains a challenge. Additional avenues for future work include extending the model to capture a second order synaptic response kernel, and time delays \parham{at lower spatial resolutions}.  The estimation techniques should also be extended to deal with spatial and temporal heterogeneity in the kernel. Finally, the majority of our current work involves applying this framework to collected data, primarily for the use of seizure detection and mitigation.}
